{\bf Affine.m} -- {\it Mathematica} package for Lie algebras of finite, affine and extended affine type

### 2011-04-04 AffineLieAlgebras/CPC/article.tex
Projection, Dynkin indices, orthogonal subsystem and some documentation in datastructures.m Sections in thesis. Small example in CPC paper.

@@

Central data structures of our package are {\it finiteWeight} and {\it affineWeight}. These structures are used to represent weights of finite-dimensional and affine Lie algebras. We have implemented several constructors for convenience of users, so weights can be specified by the coordinates in standard orthogonal basis, Dynkin labels or coefficients of decomposition to the sum of simple roots. We introduce arithmetic operations on the structures of weight and inner product (Killing form) is represented by a built-in dot-product operation.

>>>>

Weights can be specified by coordinates in standard basis or by Dynkin labels. The latter way is preferable. 
\begin{lstlisting}
  makeFiniteWeight[{1,0}]

  weight[b2][1,1]

  weight[b2a][1,0,1]
\end{lstlisting}

@@
